Class Paper - Introduction to Bayesian Statistics

### 2019-04-28 Paper_Output.Rmd
Finished paper! Wrote introduction + spell-checking

---
title: "Class Paper - Introduction to Bayesian Statistics"
author: "Ben Mainwaring"
date: "4/23/2019"
output: html_document
---

@@

Introductory summary paragraph here...

@@

The rise of right-populist parties is arguably the most important shift in European politics over the past decade. This is an important empirical shift, as it has disrupted long-standing patterns of party competition and models of voting behaviour. It is also an important normative shift. For many people with broadly liberal political views, right-populist parties are a threat to be countered. Immigration is often seen as one of the issues driving the rise of right-populist parties; if this is true, minimising anti-immmigrant sentiment might weaken these parties' standing. Governments that are opposed to (or threatened by) right-populists challengers could conceivably craft immigration and integration policy in a way that minimises sympathy for right-populist parties.

@@

Understanding the balance between these two effects is methodologically challenging. Bayesian approaches cannot solve all the methodological challenges, but may be useful in addressing some of them. This paper takes very simple Bayesian approach to measure the relationship between exposure to diversity and support for right-populist parties, testing the threat and contact hypotheses. It is a "toy" paper, designed only to illustrate a statistical approach. It does *not* adequately address other methodological issues, such as selection effects and conceptually approrpiate measurement of the variables. As such, its findings should not be taken seriously. However, it might serve as a base for "serious" future research.

@@

First, Bayesian estiamtion is technically convenient for many models used to explore the subject. "Exposure to immigrants" is often measured using geographic proximity to immigrants as a (flawed) proxy; this involves a hierarchical/multilevel model that relates individual-level attitudes or behaviours to neighbourhood- or municipal-level demographic composition. Bayesian estimation is common for hierarchical/multilevel models.[^2] The underlying theory of hierarchical models also fits well with Bayesian theory, because both assume that observed parameters are drawn from underlying distributions.

Second, a Bayesian approach allows for the incorporation of prior information into a model. Given the massive volume of research and popular commentary on right-populist parties, this is potentially valuable - a new analysis of right-populist support does not exist in a vacuum. Information on the drivers of right-populist support in one context (a given election, or a given country) can be used to more precisly estimate drivers in a different context. While the balance between threat and contact effects is debated, there is relative clarity about some other correlates of right-populist voting. For example, most politically-aware Europeans (or political scientists) would probably anticipate that right-populist support is associated with lower levels of education. Incorporating all relevant information can help build a good model, and formalising background background knowledge helps do this.

Bayesian estimation can also easily accomodate missing data patterns which are likely to occur when analysing right-populist parties. Political preferences are sensitive, and some people refuse to disclome them in surveys; the people who refuse to answer sensitive questions are likely to be systematically different from those who do. If missingness is a function of observed data, [^3] Bayesian techniques can easily produce valid and precise estimates. They are particularly flexible when the missing data is on a dependent variable, as in a model that predicts party favourability.

@@

I measure the relationship between exposure to immigrants and support for right-populist parties, primarily using Bayesian estimation but contrasing this with maximum-likelihood estimation. My case study is the Alternative for Deutschland (AfD), the main right-populist party in Germany, at the time of the German 2017 federal elections. The case selection is mostly arbitrary. However, Germany is the European Union's largest country (by population and economy), and the success or failure of right-populist parties in Germany arguably has particular importance for the rest of the world and continent. Germany is also one of Europe's most ethnically diverse countries, and the center of the post-2015 immigration wave.

Attitudinal data is taken from the 2017 cross-sectional components of the German Longitudinal Election Study (GLES), a publicly-available, reputable source of opinion data.[^4] Fieldwork in the GLES was conducted face-to-face using, using a nationally representative sampling frame. Because the GLES includes both pre- and post-election waves, it is easy to incorporate prior information without compiling data from multiple sources. Most of the analysis focuses on the post-election wave (how people *actually* voted), but priors for this wave were set based on analysis of the pre-election wave. I combine the German Election Study with data on the German election constituencies, obtained from the Federal Returing Officer (elections office) of the German government.[^5]

@@

Exposure to immigrants is measured using a proxy of local immigrant population, as is common in the literature - specifically, the proportion of the local population with a migration background. so this is a widely-used proxy. "Local" is defined as a parliamentary constituency (wahlkreis); there are a total of `r nrow(kreiseData)` constituencies in Germany. In an average constituency, about `r round(mean(kreiseData$MigrantBackground_Yes_Pct))`% of the population has a migrant background, as seen below. While constituencies vary somewhat in size, the total proportion German residents with a backgrond remains `r round(sum(kreiseData$Pop_Total_Count * kreiseData$MigrantBackground_Yes_Pct) / sum(kreiseData$Pop_Total_Count))`%.

@@

To isolate the effect of exposure to immigrants, it is necessary to include a number of control variables at both the individual and constituency level. The proportion of immigrants in a constituency is likely to vary with other socioeconomic character. The model therefore controls for constituency GDP per capita, unemployment rate, education levels (proportion of the adult population with university entracne qualificaitons), and age structure (proportion of the population aged 60 or above). Good measurement also requires separating the effect of an individiual's *own* demographic characteristics. The model includes individual parallels to the constituency-level variables described above: education, income, and employment status. It also includes a group-level control for constituency AfD vote share in 2017: it is not very interesting to say that people in AfD-supporting constituencies are more pro-AfD, so this control is necessary. Education was coded with dummies for "low" and "medium" education levels; income was coded as a quasi-continuous 13-level variable; and age was treated as a continuous variable, including a quadratic term. [^6]

@@

To formally test the above hypotheses, I build a multilevel random-intercepts model. Use i to denote individual survey respondents, and j to denote constituencoes, so that j|i denotes the constituency for the ith respondent. $\Gamma$ and $\beta$ are vectors of coefficients, while $X^{l0}$ and $X^{l1}$ are matrices of the individual-level ("level-0") and group-level ("level-1") independent variables.

@@

Priors for the post-election model were therefore specified using a multivariate normal distribution, based on the poseteriors means and covariance matrix from the pre-election survey. Covariances for both $\beta$ and $\Gamma$ coeffiients were combined into a single covariance matrix. This choice was guided partially by theory, and partially by practically. The pre-election data (below) show high covariance between elements of $\Gamma$ variables, and between a few elements of $\beta$ with a few elements of $\Gamma$. There was also very high covariance between $\beta_{age}$ and $\beta_{age^{2}}$. Under these circumstances, at least some multivariate normal specifications seem useful; they have *potential* to speed model estimation and incorporate useful prior knowledge into the analysis. Specifying all variables as part of a multivariate distribution was judged as more practical than specifying an esoteric mix of univariate and multivariate priors.

@@

The pre-election survey itself requires priors. For control variables, these were loose guesses, specified in the form of univariate normal distributions. Univariate distirbutions were chosen because there was no clear information that would suggest correlated estimates of $\beta$ and $\Gamma$; given this, univariate normal distributions were expected to be computationally easier and produce narrower posteriors. I expected that the AfD would perform better in poorer and less-educated constituencies, with higher unemployed and a more elderly population; likewise, I expected that AfD would be viewed more positively by poorer, less-educated, and unemployed people, and by men.

These expectations were codified using loose rules of thumb for both the constituency and individual level. Priors for $\Gamma$ (at the constituency level) assumed that a shift from the 25th and 75th percentiles of the IV would correspond with a 1-point shift in the DV. [^7] Priors on $\beta$ (at the individual level) used a similar rule of thumb: each variable mwould have an approximately 1-point effect. [^8] Standard deviations on the priors were intentionally broad, to reflect that they were no more than educated guesses.

@@

If this model were my main focus, I might have run with a longer number of iterations and higher thinning paramenter. However, the primary goal of analysing pre-election data is to generate a prior for use with post-election data. A quick initial run is sufficient for this purpose; narrow  standard errors on coefficient estimates are not particularly important. Even with this initial run, the credibility interval for age and age ^2^ lies outside zero, as shown in the output below.

@@

The effects of wakhlkreise-level variables are more surprising. Only two of the five variables have credibility intervals that lay entirely outside zero. This might be explained by the smaller number of observations for wahlkreise, or by the substantively smaller influence of constituency-level variabes: your neighbours' age, gender, and socioeconomic status are likely to have a smaller effect than your own personal status. One of the two nonzero Gamma coefficients (age) is in the expected direction: older parliamentary constituencies are more pro-AfD. The other (income) runs in an unexpected direction: wealthier parliamentary constituencies are also more pro-AfD. The finding regarding income does not fit easily with either threat or contact hypotheses runs contrary to both the contact and threat hypotheses. The contact the hypothesis would predict little relationship between constituency wealth and political views, while the threat hypothesis might expect that economically-secure communities would worry less about migrants.

@@

The post-election model was calculated with `r format(iterations.post, big.mark = ",")` iterations and a thinning parameter of `r thin.post`, following a `r format(burnin.post, big.mark = ",")`-iteration burn-in period. Initial diangnostics, run on a much shorter Markov Chain, suggested this was neccessary to handle severe autocorrelation problems. Even with a very long model estimation, autocorrelation was an issue for Gamma parameters, and the Beta parameters related to age, as shown below (autocorrelations plots are arbitrarily taken from the first chain, but all chains show a similar pattern).

@@

An even longer run of the Markov chain might resolve these problems. This might require the use of parallelization and distributed computing. Alternatively, it might be pragmatic to drop the quadratic age term. Age could instead be specified as a categorical variable, with categories implied by the findings of a simple linear regression with quadratic term. For present purposes, I accept the Markov Chain shown above as "good enough."

@@

Given that these results are somewhat surprising, I considered whether an incorrectly specified prior might be at fault. There would be little justification for setting a different prior *mean*, given that coefficients in the pre-election analysis were very robusrt to different priors. There could be a stronger case for setting a difference prior *variance*. The post-election survey suggests a coefficient above zero, while the pre-election survey suggests an effect below zero. Reducing the influence of the prior might lead to a coefficient whose credibility interval is above zero. However, given the long estimation time for this model, I was unable to explore alternate priors fully.

@@

Analysis of the post-election survey also finds an unexpected *negative* relationship between AfD vote in a constituency and an individual's favourability towards AfD. People in AfD-supporting communities are, on average, *less* favourable to the AfD. This seems illogical. It is possible that this result represents some statistical fluke, or the ommmission of a needed control variable. However, assuming the result is genuine, it might represent a pattern of polarisation. In places where the AfD is weak, it is less threatening -- and people are more likely to hold "soft" views towards it. [^11] While this paper assumed that AfD favourability would be a useful proxy for vote, and could ease model estimations, these findings challenge that assumption. It might be worth specifying a model with (reported) vote as the dependent, to test this assumption.

@@

The most likely substantive explanation might be be that older *communities*, rather than older *individuals*, lean towards right-populism in Germany? More "extreme" right parties, like Germany's NPD or the United Kingdom's BNP and EDL, are seen to draw support from a base of younger, working-class men. Younger, working-class men in constituencies with aging demographics -- and a social enviorment that views immigrants as threat, regardless of their numbers -- might be the AfD's true core base. These conclusions should not be drawn from a "toy" paper that ignores causal inference problems. However, if similar findings were to occur under a more robust inference strategy, they would raise interesting questions.

##Conclusions

Dolor sapiente consequatur aut error dolorem ut eum. Qui quod molestiae ut. Delectus libero quis ut placeat. Similique delectus dolores vitae nemo. Dolores officiis cum et reprehenderit perferendis iusto.

@@

[^4]: Information on the GLES is available at http://gles.eu/wordpress/english/. Data is availabe from https://www.gesis.org/en/elections-home/gles/data/ (files ZA6800, ZA6801, ZA6802). Although face-to-face research is generally seen as a "gold standard," one caveat is that fieldwork for both pre- and post-eleciton waves was conducted over a time period of more than 2 months. It is possible that vote intent/recall might shift over this period, in ways that affect findings.

@@

[^6]: "Low" education include Hauptschule graduates, and those who have not completed secondary school; "Medium" include Reaclschule graduates. Income is coded as "below 500 euros/month", then in 250 euro bands between until 1500/month, 500 euro bands until 3000/month, 1000 euro bands until 5000/month, 25000 euro bands until 10000/month, and a final "over 10000 euros/month" category.

@@

[^10]: The use of a multivariate normal prior, rather multiple univariate normal priors, was intended to speed convergence and increase accuracy. It is not clear whether this achieved its intended purpose. Benchmarking speed and autocorrelation under several model specifications would be an interesting excercise; however, it is beyond the scope of the present paper.

@@

>>>>

---
title: "Class Paper - Introduction to Bayesian Statistics"
author: "Ben Mainwaring"
date: "4/28/2019"
output:
  html_document: default
  word_document: default
---

@@

Using Bayesian methods, I build a model to analyse how exposure to immigrants affects support for right-populist parties. The model specified is a hierarchical model (with individual-level and constituency-level variables), which handles missing data on a limited number of variables. Bayesian approaches are ideal for this purpose, because it allows the incorporation of data from a *pre*-election surveys into a model of attitudes at the election. The model is applied to measure support for the German right-populist Alternative for Deutschland (AfD) around the 2017 German election.

The effect of individual-variables is generally in line with existing literature and popular commentary: the AfD is seen more favourably amongst men, less-educated people, and older people. However, the influence of constituency-level variables on political views is less intuitive. I do not find that the exposure to people with immigrant backgrounds is associated with support for AfD. However, living in constituency with an older population is associated with support for AfD. In some cases, living in a constituency with more AfD voters is *negatively* associated with support for the AfD. This might suggest a pattern of heightened polarisation in pro-AfD areas. However, it might also suggest methodological problems - either issues with parameter estimation, or broader issues with the selection of control variables or with causal inference. Challenges with convergence on one variable (age, which included a quadratic term) raised particularly concerns during estimation.

This model is therefore a "toy" starting point for exploration of Bayesian methods. Exploration of alternate variable specifications; incorporation of new controls and robustness checks; and possibly a longer run of the Markov Chain are needed. A stronger theory could also guide the development of an effective model, especially because the computationally-intensive models limit the opportunity for *ad hoc* experimentation. The initial results raise intriguing but uncertain results for speculation.

@@

The rise of right-populist parties is arguably the most important shift in European politics over the past decade. This is an important empirical shift, as it has disrupted long-standing patterns of party competition and models of voting behaviour. It is also an important normative shift. For many people with broadly liberal political views, right-populist parties are a threat to be countered. Immigration is often seen as one of the issues driving the rise of right-populist parties; if this is true, minimising anti-immigrant sentiment might weaken these parties' standing. Governments that are opposed to (or threatened by) right-populists challengers could conceivably craft immigration and integration policy in a way that minimises sympathy for right-populist parties.

@@

Understanding the balance between these two effects is methodologically challenging. Bayesian approaches cannot solve all the methodological challenges, but may be useful in addressing some of them. This paper takes very simple Bayesian approach to measure the relationship between exposure to diversity and support for right-populist parties, testing the threat and contact hypotheses. It is a "toy" paper, designed only to illustrate a statistical approach. It does *not* adequately address other methodological issues, such as selection effects and conceptually appropriate measurement of the variables. As such, its findings should not be taken seriously. However, it might serve as a base for "serious" future research.

@@

First, Bayesian estimation is technically convenient for many models used to explore the subject. "Exposure to immigrants" is often measured using geographic proximity to immigrants as a (flawed) proxy; this involves a hierarchical/multilevel model that relates individual-level attitudes or behaviours to neighbourhood- or municipal-level demographic composition. Bayesian estimation is common for hierarchical/multilevel models.[^2] The underlying theory of hierarchical models also fits well with Bayesian theory, because both assume that observed parameters are drawn from underlying distributions.

Second, a Bayesian approach allows for the incorporation of prior information into a model. Given the massive volume of research and popular commentary on right-populist parties, this is potentially valuable - a new analysis of right-populist support does not exist in a vacuum. Information on the drivers of right-populist support in one context (a given election, or a given country) can be used to more precisely estimate drivers in a different context. While the balance between threat and contact effects is debated, there is relative clarity about some other correlates of right-populist voting. For example, most politically-aware Europeans (or political scientists) would probably anticipate that right-populist support is associated with lower levels of education. Incorporating all relevant information can help build a good model, and formalising background knowledge helps do this.

Bayesian estimation can also easily accommodate missing data patterns which are likely to occur when analysing right-populist parties. Political preferences are sensitive, and some people refuse to disclose them in surveys; the people who refuse to answer sensitive questions are likely to be systematically different from those who do. If missingness is a function of observed data, [^3] Bayesian techniques can easily produce valid and precise estimates. They are particularly flexible when the missing data is on a dependent variable, as in a model that predicts party favourability.

@@

I measure the relationship between exposure to immigrants and support for right-populist parties, primarily using Bayesian estimation but contrasting this with maximum-likelihood estimation. My case study is the Alternative for Deutschland (AfD), the main right-populist party in Germany, at the time of the German 2017 federal elections. The case selection is mostly arbitrary. However, Germany is the European Union's largest country (by population and economy), and the success or failure of right-populist parties in Germany arguably has particular importance for the rest of the world and continent. Germany is also one of Europe's most ethnically diverse countries, and the center of the post-2015 immigration wave.

Attitudinal data is taken from the 2017 cross-sectional components of the German Longitudinal Election Study (GLES), a publicly-available, reputable source of opinion data.[^4] Fieldwork in the GLES was conducted face-to-face using, using a nationally representative sampling frame. Because the GLES includes both pre- and post-election waves, it is easy to incorporate prior information without compiling data from multiple sources. Most of the analysis focuses on the post-election wave (how people *actually* voted), but priors for this wave were set based on analysis of the pre-election wave. I combine the German Election Study with data on the German election constituencies, obtained from the Federal Returning Officer (elections office) of the German government.[^5]

@@

Exposure to immigrants is measured using a proxy of local immigrant population, as is common in the literature - specifically, the proportion of the local population with a migration background. so this is a widely-used proxy. "Local" is defined as a parliamentary constituency (wahlkreis); there are a total of `r nrow(kreiseData)` constituencies in Germany. In an average constituency, about `r round(mean(kreiseData$MigrantBackground_Yes_Pct))`% of the population has a migrant background, as seen below. While constituencies vary somewhat in size, the total proportion German residents with a background remains `r round(sum(kreiseData$Pop_Total_Count * kreiseData$MigrantBackground_Yes_Pct) / sum(kreiseData$Pop_Total_Count))`%.

@@

To isolate the effect of exposure to immigrants, it is necessary to include a number of control variables at both the individual and constituency level. The proportion of immigrants in a constituency is likely to vary with other socioeconomic character. The model therefore controls for constituency GDP per capita, unemployment rate, education levels (proportion of the adult population with university entrance qualifications), and age structure (proportion of the population aged 60 or above). Good measurement also requires separating the effect of an individual's *own* demographic characteristics. The model includes individual parallels to the constituency-level variables described above: education, income, and employment status. It also includes a group-level control for constituency AfD vote share in 2017: it is not very interesting to say that people in AfD-supporting constituencies are more pro-AfD, so this control is necessary. Education was coded with dummies for "low" and "medium" education levels; income was coded as a quasi-continuous 13-level variable; and age was treated as a continuous variable, including a quadratic term. [^6]

@@

To formally test the above hypotheses, I build a multilevel random-intercepts model. Use i to denote individual survey respondents, and j to denote constituencies, so that j|i denotes the constituency for the $i^{th}$ respondent. $\Gamma$ and $\beta$ are vectors of coefficients, while $X^{l0}$ and $X^{l1}$ are matrices of the individual-level ("level-0") and group-level ("level-1") independent variables.

@@

Priors for the post-election model were therefore specified using a multivariate normal distribution, based on the posteriors means and covariance matrix from the pre-election survey. Covariances for both $\beta$ and $\Gamma$ coefficients were combined into a single covariance matrix. This choice was guided partially by theory, and partially by practically. The pre-election data (below) show high covariance between elements of $\Gamma$ variables, and between a few elements of $\beta$ with a few elements of $\Gamma$. There was also very high covariance between $\beta_{age}$ and $\beta_{age^{2}}$. Under these circumstances, at least some multivariate normal specifications seem useful; they have *potential* to speed model estimation and incorporate useful prior knowledge into the analysis. Specifying all variables as part of a multivariate distribution was judged as more practical than specifying an esoteric mix of univariate and multivariate priors.

@@

The pre-election survey itself requires priors. For control variables, these were loose guesses, specified in the form of univariate normal distributions. Univariate distributions were chosen because there was no clear information that would suggest correlated estimates of $\beta$ and $\Gamma$; given this, univariate normal distributions were expected to be computationally easier and produce narrower posteriors. I expected that the AfD would perform better in poorer and less-educated constituencies, with higher unemployed and a more elderly population; likewise, I expected that AfD would be viewed more positively by poorer, less-educated, and unemployed people, and by men.

These expectations were codified using loose rules of thumb for both the constituency and individual level. Priors for $\Gamma$ (at the constituency level) assumed that a shift from the 25th and 75th percentiles of the IV would correspond with a 1-point shift in the DV. [^7] Priors on $\beta$ (at the individual level) used a similar rule of thumb: each variable would have an approximately 1-point effect. [^8] Standard deviations on the priors were intentionally broad, to reflect that they were no more than educated guesses.

@@

If this model were my main focus, I might have run with a longer number of iterations and higher thinning parameter. However, the primary goal of analysing pre-election data is to generate a prior for use with post-election data. A quick initial run is sufficient for this purpose; narrow  standard errors on coefficient estimates are not particularly important. Even with this initial run, the credibility interval for age and age ^2^ lies outside zero, as shown in the output below.

@@

The effects of wakhlkreise-level variables are more surprising. Only two of the five variables have credibility intervals that lay entirely outside zero. This might be explained by the smaller number of observations for wahlkreise, or by the substantively smaller influence of constituency-level variables: your neighbours' age, gender, and socioeconomic status are likely to have a smaller effect than your own personal status. One of the two nonzero Gamma coefficients (age) is in the expected direction: older parliamentary constituencies are more pro-AfD. The other (income) runs in an unexpected direction: wealthier parliamentary constituencies are also more pro-AfD. The finding regarding income does not fit easily with either threat or contact hypotheses runs contrary to both the contact and threat hypotheses. The contact the hypothesis would predict little relationship between constituency wealth and political views, while the threat hypothesis might expect that economically-secure communities would worry less about migrants.

@@

The post-election model was calculated with `r format(iterations.post, big.mark = ",")` iterations and a thinning parameter of `r thin.post`, following a `r format(burnin.post, big.mark = ",")`-iteration burn-in period. Initial diagnostics, run on a much shorter Markov Chain, suggested this was necessary to handle severe autocorrelation problems. Even with a very long model estimation, autocorrelation was an issue for Gamma parameters, and the Beta parameters related to age, as shown below (autocorrelations plots are arbitrarily taken from the first chain, but all chains show a similar pattern).

@@

An even longer run of the Markov chain might resolve these problems. This might require the use of parallelisation and distributed computing. Alternatively, it might be pragmatic to drop the quadratic age term. Age could instead be specified as a categorical variable, with categories implied by the findings of a simple linear regression with quadratic term. For present purposes, I accept the Markov Chain shown above as "good enough."

@@

Given that these results are somewhat surprising, I considered whether an incorrectly specified prior might be at fault. There would be little justification for setting a different prior *mean*, given that coefficients in the pre-election analysis were very robust to different priors. There could be a stronger case for setting a difference prior *variance*. The post-election survey suggests a coefficient above zero, while the pre-election survey suggests an effect below zero. Reducing the influence of the prior might lead to a coefficient whose credibility interval is above zero. However, given the long estimation time for this model, I was unable to explore alternate priors fully.

@@

Analysis of the post-election survey also finds an unexpected *negative* relationship between AfD vote in a constituency and an individual's favourability towards AfD. People in AfD-supporting communities are, on average, *less* favourable to the AfD. This seems illogical. It is possible that this result represents some statistical fluke, or the omission of a needed control variable. However, assuming the result is genuine, it might represent a pattern of polarisation. In places where the AfD is weak, it is less threatening -- and people are more likely to hold "soft" views towards it. [^11] While this paper assumed that AfD favourability would be a useful proxy for vote, and could ease model estimations, these findings challenge that assumption. It might be worth specifying a model with (reported) vote as the dependent, to test this assumption.

@@

The most likely substantive explanation might be that older *communities*, rather than older *individuals*, lean towards right-populism in Germany? More "extreme" right parties, like Germany's NPD or the United Kingdom's BNP and EDL, are seen to draw support from a base of younger, working-class men. Younger, working-class men in constituencies with aging demographics -- and a social environment that views immigrants as threat, regardless of their numbers -- might be the AfD's true core base. These conclusions should not be drawn from a "toy" paper that ignores causal inference problems. However, if similar findings were to occur under a more robust inference strategy, they would raise interesting questions.

##Next Steps

Three steps are be necessary in order to strengthen the inference strategy, and draw clear conclusions from the results. First, issues with model estimation, related the problematic $\beta{age}$ and  $\beta{age^{2}}$ terms, should be resolved. It is possible that the literature has guidance on handling quadratics; and also possible quadratics simply do not work well with Bayesian models. Specifying priors for these variables differently; or else adopting an entirely functional form (such as a series of categorical dummies).

Second, additional model specifications should be explored. The control for district-level AfD vote seems necessary [^12], but complicates interpretation and should be considered more carefully. Initial exploration, using pre-election data, shows that the omission of constituency vote share does not greatly affect findings for other variables; however, this has not been thoroughly explored. Constituency was chosen as a convenient level of analysis, but neighbourhood or municipal-level characteristics might actually have a larger effect on political attitudes. People's views are likely to be shaped by the places where they spend their daily lives. More generally, controls were chosen arbitrarily, and might not be ideal. Measures of occupational class, religiosity, and housing status might be relevant; at an aggregate level, the distinction between East and West German states might also be relevant. A good strategy for estimating quadratic terms would aid in the exploration of additional specifications, because it could greatly speed model estimation and therefore make robustness checks practical.[^13]

Finally, the broader issues around selection bias and causal inference must be addressed. This is a separate question, outside Bayesian estimation. It is one that the literature has rarely answered in a satisfactory manner. The use of large-scale panel data is one possible solution. Showing how peoples' political views change *after* they move to more diverse neighbourhoods or workplaces would provide stronger evidence. This requires access to relatively rare data sources, but may not be impossible. Good research design should start with "what is ideal" and *then* move to "what is achievable."

There are three purely methodological challenges that this paper did not explore in great depth - but that a longer version would ideally explore. First, the paper uses both univariate and multivariate priors, but does not systematically compare their results. Benchmarking these two approaches (both their "accuracy" and their computational speed) would be interesting. This paper also implements basic missing-data handling -- but does not implement complicated imputation models, or compare fully Bayesian imputation with conventional (semi-Bayesian?) multiple imputation. This would be a useful extension. Finally, the paper currently does not consider any model selection or hypothesis testing techniques. Given the relatively simple hypotheses considered, these are probably not strictly necessary -- but they would nonetheless be a useful exercise. There are many topics to explore, both substantively and methodologically, following this initial work.

@@

[^4]: Information on the GLES is available at http://gles.eu/wordpress/english/. Data is available from https://www.gesis.org/en/elections-home/gles/data/ (files ZA6800, ZA6801, ZA6802). Although face-to-face research is generally seen as a "gold standard," one caveat is that fieldwork for both pre- and post-election waves was conducted over a time period of more than 2 months. It is possible that vote intent/recall might shift over this period, in ways that affect findings.

@@

[^6]: "Low" education include Hauptschule graduates, and those who have not completed secondary school; "Medium" include Realschule graduates. Income is coded as "below 500 euros/month", then in 250 euro bands between until 1500/month, 500 euro bands until 3000/month, 1000 euro bands until 5000/month, 25000 euro bands until 10000/month, and a final "over 10000 euros/month" category.

@@

[^10]: The use of a multivariate normal prior, rather multiple univariate normal priors, was intended to speed convergence and increase accuracy. It is not clear whether this achieved its intended purpose. Benchmarking speed and autocorrelation under several model specifications would be an interesting exercise; however, it is beyond the scope of the present paper.

@@

[^12]: It is logically necessary that people in an AfD-supporting constituency are more likely to be AfD supports. Constituency-level variables that are correlated with AfD vote share would therefore *appear* correlated with individual-level AfD support, even if the correlation is spurious.

[^13]: Informal experimentation with various sets of variables is often a part of model-building. Computationally intensive models impose discipline, by containing experimentation. This can be helpful, because it avoids overfitting and demands good theory. However, it might require a stronger theory than I had when pursuing this project.
